\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Software Architect}
    {CareEvolution}
    {Full Time Remote}
    {March 2015 - Present}
    {
      \begin{cvitems}
        \item {Architected and own the AWS platform (multi-account, multi-VPC) behind Orchestrate, CareEvolution's cloud-native healthcare data-integration product (Terminology, Convert, Insight, and Identity APIs) used across 200M+ lives; the gateway serves 5.5M+ connections per quarter, including a terminology API processing 890M+ translations per quarter (3.6B/year) at 13.4 requests/sec sustained.}
        \item {Built the Kong API gateway and its custom Lua permissions plugin (downstream-signed JWT authorization), with usage tracking and freemium tier enforcement (free 100-request tier and paid tiers) via declarative config and Lambda.}
        \item {Engineered a from-scratch gateway replacement in .NET 10 \& YARP, sole author (around 39K LOC, 435 tests), featuring AWS Lambda request proxying and KMS-envelope-encrypted API keys.}
        \item {Built a keyless (OIDC) CI/CD platform with self-service ephemeral per-pull-request environments: dedicated ECS services, Postgres databases, and header-routed ALB rules with automated smoke tests and teardown, plus CodeDeploy blue/green production deploys on merge.}
        \item {Hardened software delivery across services: SHA-pinned, least-privilege GitHub Actions gated by zizmor and actionlint with findings surfaced in GitHub Advanced Security; distroless, read-only-root-filesystem, capability-dropped containers on ARM64/Graviton Fargate.}
        \item {Own cloud infrastructure-as-code across 15+ AWS accounts: 93K+ lines of Terraform/OpenTofu and 150+ reusable modules on Terragrunt, with Control Tower and IAM Identity Center SSO.}
        \item {Drove org-wide security and compliance posture: DNSSEC across all zones, AWS Security Hub, FIPS ALB policies, WAF, default encryption, and Tenable/Nessus vulnerability-scanning infrastructure.}
        \item {Designed serverless services including a credential-management API with saga-style consistency and per-customer KMS keys, and an AWS-to-Azure event bridge (Kinesis to Event Grid) with automated secret rotation.}
        \item {Led the caching and service-authentication workstream for an internal healthcare event-query platform (ASP.NET Core, React): a Redis L2 cache with a Lambda cache-writer, and a migration of service-to-service auth to AWS VPC Lattice (API Gateway principal patterns and SigV4 request signing).}
        \item {Own logging, metrics, and tracing across the platform: implemented and maintained Splunk, plus OpenTelemetry/ADOT and Prometheus instrumentation.}
        \item {Own the React front end for the Orchestrate developer portal and a UI-gated sandbox proxy offering free, quota-exempt API trials; also own self-service SFTP provisioning via AWS Transfer Family and SQL ingestion pipelines processing billions of records under a contractual client SLA.}
        \item {Earlier: feature owner for RKStudio, a clinical-research study platform within MyDataHelps: access control, organization settings, localization, blinded-study mode, and survey authoring, plus HIPAA-oriented security hardening (Veracode remediation, patient access policies).}
        \item {Owned core subsystems of SupportCentral, an internal healthcare monitoring platform: a CQRS request/authorization pipeline, Roslyn-scripted monitoring sensors, Prometheus observability, and multi-channel alerting (Slack, PagerDuty, email).}
        \item {Built internal automation in Rust (AWS Lambda on Graviton) for multi-tenant resource cleanup and Kong/Cognito user-inventory compliance reporting.}
      \end{cvitems}
    }
  \cventry
    {Enterprise Architect}
    {Servpro Industries}
    {Gallatin, TN}
    {March 2014 - March 2015}
    {
      \begin{cvitems}
        \item {Took over maintenance of Servpro's mobile app (Objective-C \& JavaScript on Apache Cordova) within the first month, then found and fixed several major performance issues in a new flagship product.}
        \item {Won the department's rock star award the first period I was eligible; promoted to architect within the first year.}
      \end{cvitems}
    }
  \cventry
    {Senior Software Developer}
    {Little Lambs Fundraising}
    {Gallatin, TN}
    {August 2010 - March 2014}
    {
      \begin{cvitems}
        \item {Built integration and automation across warehouse and ordering systems: barcode picking for accuracy, multi-channel delivery notifications (call, text, email), and a Django CRM/order-entry system.}
        \item {Owned all IT systems and decisions.}
      \end{cvitems}
    }
  \cventry
    {Software Developer}
    {Cracker Barrel Old Country Store}
    {Lebanon, TN}
    {August 2004 - August 2010}
    {
      \begin{cvitems}
        \item {Developed and maintained a PCI-compliant credit-card processing system in RPGLE on an iSeries server, interfacing with the Infinium package.}
        \item {Built custom HR/Financial software (PHP, C\#, ASP.net) and integrated E-Verify with the existing HR system.}
      \end{cvitems}
    }
\end{cventries}
